Group 9 Presentation

### 2021-12-07 presentation.Rmd
New Slides

---
title: "Group 9 Presentation"
author: "Henrique, Oriana, Jorie"
date: "12/4/2021"
output:
  beamer_presentation: default
  ioslides_presentation: default
---

>>>>

---
title: "Group 9 Presentation"
author: "Henrique, Oriana, Jorie"
date: "12/4/2021"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---
